Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
Updated definitions for blur and aggregation

TODO settings and images
The zoom level is a slice plane through our three dimensional space. 
TODO define parent child
The results can be found in figure ~\ref{fig:Zoom}.
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

@@

The evaluation results are plotted in Fig.~\ref{fig:Blur}, each point in
the graph represents the \SOHUP metric (Eq.\ref{eq:SoH-up}) between two
$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
has a fixed size of $41{\times}41$

\begin{displaymath}
\SOHUP( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
\end{displaymath}

The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. $G^*$ doesn't fit to the mean of our whiskerplot.

>>>>

The aggregation level is a slice plane through our three dimensional space. 
We evalute only the aggregation with fixed W and fixed F.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

The results can be found in figure ~\ref{fig:Zoom}.
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

@@

Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}.
The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. 
$G^*$ doesn't fit to the mean of our whiskerplot.
